\documentclass[12pt]{article}
\setlength{\textheight}{9.1 in}
\setlength{\textwidth}{6.4 in}
\setlength{\oddsidemargin}{-0.25 cm}
\setlength{\topmargin}{-0.3 cm}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancy}
\fancyhead{}
\renewcommand{\headrulewidth}{0.pt}
\lfoot{\small Jason Melbourne}
\rfoot{\small NSF Postdoc Bio Sketch}
\cfoot{\thepage/2}
\begin{document}

\begin{center}
Biographical Sketch\\
{\Large\bf{Jason Melbourne}}\\
\textnormal
Graduate Student University of California Santa Cruz
\end{center}

\noindent
{\bf{Professional Preparation}}

\vspace{12pt}

\begin{tabular}[h]{lcr}
University of California Berkeley & Physics and Astronomy  & B.A. 1995 \\
Wesleyan University & Astronomy & M.A. 1999 \\
University of California Santa Cruz & Astronomy & Ph.D. 2006\\
\end{tabular}

\vspace{12pt}

\noindent
{\bf{Publications}} \\
\emph{Relevant  to Proposal}
\begin{itemize}{ }
\addtolength{\itemsep}{-0.25cm}

\item Melbourne, J., Koo, D. C., Le Floc’h, E. ``Optical Morphology Evolution of Infrared Luminous Galaxies in GOODS-N''. \emph{The Astrophysical Journal Letters}. Accepted for Publication, 2005

\item Melbourne, J., Wright, S. A., Barczys, M., Bouchez, A. H., Chin, J., van Dam, M. A., Hartman, S., Johansson, E., Koo, D. C., Lafon, R., Larkin, J., Le Mignant, D., Lotz, J., Max, C. E., Pennington, D. M., Stomski, P. J., Summers, D., Wizinowich, P. L. ``Merging Galaxies in GOODS-S: First Extragalactic Results from Keck Laser Adaptive Optics''. \emph{The Astrophysical Journal}. Volume 625, Issue 1, pp. L27-L30, 2005

\item Melbourne, J., Phillips, A., Salzer, J. J., Gronwall, C., Sarajedini, V. L. ``Metal Abundances of KISS Galaxies. II. Nebular Abundances of 12 Low-Luminosity Emission-Line Galaxies''. \emph{The Astronomical Journal}. Volume 127, Issue 2, pp. 686-703, 2004

\item Melbourne, J., Salzer, J. J. ``Metal Abundances of KISS Galaxies. I. Coarse Metal Abundances and the Metallicity-Luminosity Relation''. \emph{The Astronomical Journal}. Volume 123, Issue 5, pp. 2302-2311, 2002

\item Salzer, J. J., Lee, J. C., Melbourne, J., Hinz, J. L., Alonso-Herrero, A., Jangren, A. ``Metal Abundances of KISS Galaxies. IV. Galaxian Luminosity-Metallicity Relations in the Optical and Near-Infrared''. \emph{The Astrophysical Journal}. Volume 624, Issue 2, pp. 661-679, 2005
\end{itemize}

\noindent
\emph{Unrelated to Proposal}
\begin{itemize}{ }
\addtolength{\itemsep}{-0.25cm}

\item Melbourne, J., Guhathakurta, P. ``Measuring the Slope of the Dust Extinction Law and the Power Spectrum of Dust Clouds Using Differentially Reddened Globular Clusters''. \emph{The Astronomical Journal}. Volume 128, Issue 1, pp. 271-286, 2004

\item Melbourne, J., Sarajedini, A., Layden, A., Martins, D. H. ``CCD Photometry of the Globular Cluster NGC 4833 and Extinction Near the Galactic Plane''. \emph{The Astronomical Journal}. Volume 120, Issue 6, pp. 3127-3138, 2000 

\item Lee, J. C., Salzer, J. J., Melbourne, J. ``Metal Abundances of KISS Galaxies. III. Nebular Abundances for Fourteen Galaxies and the Luminosity-Metallicity Relationship for H II Galaxies''. \emph{The Astrophysical Journal}. Volume 616, Issue 2, pp. 752-767, 2005

\item Prochaska, J., Bloom, J. S., Chen, H., Hurley, K. C., Melbourne, J., Dressler, A.,  Graham, J. R., Osip, D. J., Vacca, W. D. ``The Host Galaxy of GRB 031203: Implications of Its Low Metallicity, Low Redshift, and Starburst Nature''. \emph{The Astrophysical Journal}. Volume 611, Issue 1, pp. 200-207, 2004

\item Wegner, G., Salzer, J. J., Jangren, A., Gronwall, C., Melbourne, J. ``Spectroscopy of KISS Emission-Line Galaxy Candidates. I. MDM Observations''. \emph{The Astronomical Journal}. Volume 125, Issue 5, pp. 2373-2392, 2003
\end{itemize}

\noindent
{\bf{Synergistic Activities}}
\begin{itemize}
\addtolength{\itemsep}{-0.25cm}
\item[2005] Organized and Chaired the The Center for Adaptive Optics Extragalactic AO Workshop, University of California Santa Cruz, August 2005.  Participants of the workshop presented extragalactic AO science, discussed observing strategies and limitations of current AO systems and established a collaborative environment among the extragalactic AO community. 
\item[2005] Mentored Emily De La Garza, Center for Adaptive Optics undergraduate summer intern.  Her project \emph{Stellar Population Synthesis Models of Synthetic Galaxies}, received first prize at the Society for Advancement of Chicanos/Latinos and Native Americans (SACNAS) annual science meeting.
\item[2005] Lead Instructor for the Center for Adaptive Optics (CFAO) Mainland Short Course for undergraduates from under-represented groups.  This week long course utilizes inquiry based teaching techniques to prepare the students for summer internships in astronomy and vision science.
\item[2005] Science advisor for the California Math and Science Partnership (CaMSP) program in Santa Cruz County.  CaMSP, sponsored by the Educational Partnership Center, matched UC Santa Cruz scientists with local middle school science teachers to integrate math into the science curriculum by means of interactive activities.   
\item[2003] Project Advisor for COSMOS, an astronomy summer program for under-represented high school students.
\end{itemize}

\noindent
{\bf{Collaborators and other Affiliations}}

\vspace{6pt}

\noindent
\emph{Collaborators and Co-Editors}

\vspace{6pt}

\noindent
Alonso-Herrero	Almudena 	U. of Arizona;
	Barczys	Matthew	UCLA;
	Bloom Joshua UC Berkeley;
	Bouchez	Antonin	Caltech;
	Chen Hsiao-Wen	MIT;
	Chin	Jason	Keck Observatory;
	Dressler Alan	Carnegie Observatories;
	Faber	Sandra	UC Santa Cruz;
	Graham James UC Berkeley;
	Gronwall	Caryl	Penn State;
	Guhathakurta	Puragra	UC Santa Cruz;
	Hartman	S.	Keck Observatory;
	Hinz	Joannah	U. Arizona;
	Hurley Kevin 	UC Berkeley;
	Jangren	Anna	Wesleyan U.;
	Johansson	E.	Keck Observatory;
	Koo	David	UC Santa Cruz;
	Lafon	Robert	Keck Observatory;
	Larkin	James	UCLA;
	Le Floc’h	Emeric	U. of Arizona;
	Le Mignant	David	Keck Observatory;
	Lee	Janice	U. of Arizona;
	Lotz	Jennifer	NOAO;
	Max	Claire	UC Santa Cruz;
	Osip David	Las Campanas Observatory;
	Pennington	Dee  LLNL;
	Phillips	Andrew	UC Santa Cruz;
	Prochaska	Jason 	UC Santa Cruz;
	Salzer	John 	Wesleyan U.;
	Sarajedini	Vicky	U. of Florida;
	Stomski	P. J.	Keck Observatory;
	Summers	D.	Keck Observatory;
	Vacca W. D.      Keck Observatory;
	van Dam	Marcos	Keck Observatory;
	Wegner	Gary 	Dartmouth College;
	Wizinowich	Peter	Keck Observatory;
	Wright	Shelley	UCLA

\vspace{6pt}

\noindent
\emph{Graduate Advisors}

\vspace{6pt}

\noindent
Koo David UC Santa Cruz (Ph.D. Thesis Advisor)\\
Salzer John	Wesleyan U. (Master's Thesis Advisor)




%{\bf{\Large Publications:}}\\
%\noindent
%Melbourne, J., Phillips, A., Salzer, J.~J. et al. ``Metal Abundances of KISS 
%Galaxies. II. Nebular Abundances of Twelve Low-Luminosity Emission-Line
%Galaxies.'' \ 2004, AJ (accepted)\\ 

%\noindent
%Melbourne, J.~\& Guhathakurta, P. ``Measuring the Slope of the Galactic
%Dust Extinction Law, $R_V$, and the Angular Power Spectrum of Dust Clouds 
%in the Direction of Differentially-Reddened Globular Clusters.'' 
%\ 2004, AJ (in prep.)\\

%\noindent
%Melbourne,
%J.~\& Guhathakurta, P. ``Measuring the Angular Power Spectrum of Dust 
%Clouds in the Direction of Differentially-Reddened Globular Clusters.''
%\ 2003, Astrophysics of Dust, Estes Park, Colorado, 
%May 26 - 30, 2003.~Edited by Adolf N.~Witt.,  \\

%\noindent
%Melbourne, J.~\& 
%Salzer, J.~J. ''Metal Abundances of KISS Galaxies. I. Coarse Metal 
%Abundances and the Metallicity-Luminosity Relation.''\ 2002, AJ, 123, 2302 \\

%\noindent
%Melbourne, J., Sarajedini, A., Layden, 
%A., \& Martins, D.~H. ``CCD Photometry of the Globular Cluster NGC 4833 
%and Extinction Near the Galactic Plane.'' \ 2000, AJ, 120, 3127 \\

%\noindent
%Deustua, S.~et al.''Supernovae''\ 
%1995, IAU CIRC, 6270, 1 \\

%\noindent
%Wegner, G., Salzer, 
%J.~J., Jangren, A., Gronwall, C., \& Melbourne, J. ``Spectroscopy of KISS 
%Emission-Line Galaxy Candidates. I. MDM Observations.''\ 2003, AJ, 125, 2373 \\


\end{document}
% LocalWords:  UC Astro Salzer al AJ Guhathakurta Metallicity Sarajedini Layden
% LocalWords:  CCD NGC Deustua IAU CIRC Wegner Jangren Gronwall MDM
