\documentclass[12pt]{article}
\begin{document}
\pagestyle{myheadings}
\markright{{\bf{Curiculum Vitae}}}
\noindent
Jason Melbourne\\
UCO/Lick Observatory\\
UC Santa Cruz\\
Santa Cruz, CA 95060\\
U.S.A.\\\\
831-459-5891\\
jmel@ucolick.org\\\\
November 6, 2003\\\\
{\bf{Education:}}\\
\noindent
$\bullet$ 1995 B.A. Physics and Astronomy, U.C. Berkeley\\
$\bullet$ 2001 M.A. Astronomy, Wesleyan University\\
$\bullet$ 2001 The Vatican Observatory Summer School\\ 
$\bullet$ 2001 - present PhD. Program at UCSC\\\\
\noindent
{\bf{Research Experience:}}\\
$\bullet$ 1992 - 1996 Photometry of Comets\\
Dr. Hy Spinrad, UC Berkeley, hspinrad@astro.berkeley.edu\\
$\bullet$ 1995 - 1996 Supernova Cosmology Project\\
Dr. Saul Perlmutter, Lawrence Berkeley National Lab, S_Perlmutter@lbl.gov\\
$\bullet$ 1999 - 2000 Globular Cluster Photometry\\
Dr. Ata Sarajedini, Wesleyan University, ata@astro.ufl.edu\\
$\bullet$ 2000 - 2003 Metal Abundances of Starforming Galaxies\\
Dr. John Salzer, Wesleyan University, slaz@astro.wesleyan.edu\\
$\bullet$ 2001 - 2003 Maping Small-Scale Structure in the ISM\\
Dr. Raja Guhathakurta, UC Santa Cruz, raja@ucolick.org\\
$\bullet$ 2002 - 2003 Adaptive Optics Imaging of Compact Galaxies\\
Dr. Claire Max, UC Santa Cruz, max@ucolick.org\\ 
Dr. David Koo, UC Santa Cruz, koo@ucolick.org\\
$\bullet$ 2003 Adaptive Optics Imaging in GEMS and GOODS\\
Dr. Claire Max, UC Santa Cruz, max@ucolick.org\\ 
Dr. David Koo, UC Santa Cruz, koo@ucolick.org\\
Dr. Sandy Faber, UC Santa Cruz, faber@ucolick.org\\
$\bullet$ 2003 Compact Galaxies in GOODS\\
Dr. Andrew Phillips, UC Santa Cruz, phillips@ucolick.org\\ 
Dr. David Koo, UC Santa Cruz, koo@ucolick.org\\\\




\end{document}